Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-09 GWLDCII.tex
changes from on the phone

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram. {\color{violet} This proof and the methods used therein are a first step towards understanding how the positroid cell assocaited to a Wilson loop diagram changes as one adds propagators in certain positions.}

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}). \hlfix{It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram;}{what does this mean?} {\color{violet} It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).} Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections {\color{violet} to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).}

@@

If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i^W$. Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as follows:
\begin{dfn}\label{def I_i as a function}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i^W : \cP \longrightarrow [n]$ by
\[I_i^W(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
for each $p \in \cP$. 
\end{dfn}

@@

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}\note{That's ok though because this remark does give the function matching in that region.}

@@

With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration}\note{Why is configuration italicized?} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

@@

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem} 
\sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: \st{either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.} {\color{violet}either $i-1 \in V(p)$, in which case it is the last vertex in the $<_i$ order and $I_i(p)= i-1$, or $i-1 \not \in V(p)$ in which case,  $p= a, b$, $i \in [b+2, a]$ and $I_i(p) = b+1$.}

@@

	\end{scope}
		\end{scope}
	\end{tikzpicture}
\] 
\caption{The two types of configuration that would (in theory) allow the propagator $p$ to contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}
In Case 1, \st{observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.}{\color{violet} since $b+1<_i I_i(p)$ there must be some propagator, $q$ before $p$ in $\cP^i$ such that $I_i(q) = b+1$. By remark \ref{clockwise ordering rem}, $p$ is inside $q$ in the $<_b$ order. Specifically, $q$ must also end on the $b^{th}$ edge. By non-crossing and desnity arguements of admissibility $i-1$ cannot be in $V(q)$.} Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2. Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range \hlfix{(since $p$ will be the final propagator encountered by the algorithm)}{Sian added this: it's not really a locally-the-same argument so I'm not sure it'll help to reference Remark 3.12} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
\note{Sian made minor edits to this proof: mostly removing those two numbered observations because one is now a remark and the other is only used once}
\begin{thm}\label{res alg gives correct GN}
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}
\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order. Therefore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$? Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$. $I_i(p_t) <_i I_i(p_s)$ certainly isn't obvious and may not be true}. {\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order \hlfix{and we are done}{not quite true; same reasoning as why we're using ``the other end of the propagator'' instead of $V(p_s) \subseteq [a_s-1, j_m]$} \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

@@

In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).  The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}\sanote{implemented, but don't like how it no longer stands out. Thoughts?}
In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.

@@

{\color{violet}More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell. }

@@

\sanote{musing: would it be worth moving the LE diagram exposition here? Do we use it ealier? I like having exposition in front generally, but it feels a mile away.}

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element\note{This is saying to increment twice in a way which I think is confusing, but presumably the parenthetical remark was put there to try to clarify something so I don't want to just remove it}.  Formally, \st{if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then}\sanote{in favor of removing parenthetical, we say same thing twice without it}
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

By Corrollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e. it must be a column label. The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$\note{I don't find the star very helpful here; different area's conventions maybe} is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$. 
\end{proof}

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $k \geq 1$ propagators.  Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering \st{(that is $i+2, \ldots, n-2$ do not support any propagators in $W'$)}.
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it, if $q$ exists in the second condition then $j<_ji<_jn-1$.

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  Then we can express $I_*^W$ in terms of $I_*^V$ as follows:\note{I'm not a fan of the case labels in this display: there's enough going on already without throwing in extra information}

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$ (Case 1)} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$ (Case 1)}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$ (Case 2)}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.

@@

\end{figure} \sanote{moved figure before theorem 4.4 so that we can just refer to generically}
\begin{proof}

We first consider $I_1^{W}$, i.e. the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e. helpful at this point, is it an old thing that can go or do others find it useful?} \sanote{agreed, i vote to cut}. Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why? isn't obvious to me without several cases, and even then}\note{yeah, I can't see this either; cyclic intervals is probably a better argument} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

>>>>

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram. This proof and the methods used therein are a first step towards understanding how the positroid cell associated to a Wilson loop diagram changes as one adds propagators in certain positions.

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}). It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}). Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).

@@

If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \textbf{contributes} $j$ to $I_i^W$. Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as follows:
\begin{dfn}\label{def I_i as a function}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i^W : \cP \longrightarrow [n]$ by
\[I_i^W(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
for each $p \in \cP$. 
\end{dfn}

@@

@@

With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

@@

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem} 
\sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.

@@

	\end{scope}
		\end{scope}
	\end{tikzpicture}
\] 
\caption{The two types of configuration that would (in theory) allow the propagator $p$ to contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}
In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$. Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2. Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
\begin{thm}\label{res alg gives correct GN}
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}
\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order. Therefore $I_i(p_t) <_i I_i(p_r)$
%{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order \hlfix{and we are done}{not quite true; same reasoning as why we're using ``the other end of the propagator'' instead of $V(p_s) \subseteq [a_s-1, j_m]$} \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}
Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

@@

In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).  The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.

@@

More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell.

@@

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.  Formally, 
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

By Corrollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e. it must be a column label. The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$. 
\end{proof}

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $k \geq 1$ propagators.  Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering.
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it, if $q$ exists in the second condition then $j<_ji<_jn-1$.

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  Then we can express $I_*^W$ in terms of $I_*^V$ as follows:

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

\begin{proof}
The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.

We first consider $I_1^{W}$. Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why? isn't obvious to me without several cases, and even then}\note{yeah, I can't see this either; cyclic intervals is probably a better argument} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
